Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-26 docs/manuscript/manuscript.tex
Removal of parentheses for variable labels.

\subsection{Model results}
First, we developed a correlation chart to quickly analyze if there is any great correlation between all the 28 numerical variables that may pertain to water accessibility. We recognized the strong and weak relationship by the size and color of the correlation plot is shown in \autoref{fig:cor-basic}, which indicates households with limited water service (liws) has the strongest and positive relationship with Households possessing a bicycle (bicy). Meanwhile, households using an improved water source (imws) has the strongest and negative relationship with households using an unimproved water source (uiws). This initial finding results indicated that the initial variables are logical and can give us insight into further understanding and the relationship between these variables.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation Graph of Numerical Variables}
  \label{fig:cor-basic}
\end{figure}
As we continued to study further upon the correlations of the variables, we used more advanced correlation graphs to determined their p-value, and to see a relationship between different categorical variables is shown in \autoref{fig:cor-plot}, which again indicates a greater detailed comparison between the variables. Households with an improved water source on the premises (iwsp) have a strong relationship with households with basic water service (basw) of .84 and a p-value of less than 0.001. Also, we learned and discovered that Households using an unimproved water source (uiws) have a positive relationship with Households using unprotected well water (uwel), Households using an unprotected spring (uspr), and Households using surface water (surw) with a p-value of less than 0.001 as well. These relationships justify the necessity to research further if the particular water accessibility variables can increase the accessibility of particular water sources to reach universal access to water by 2030, as proposed in the SDGs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Numerical Variables}
  \label{fig:cor-plot}
\end{figure}
Additionally, we wanted to explore if the modes of transportation variables have any relationship with potential water variables. Therefore, we investigated by developing more correlation plots relating transportation variables with water accessibility variables which are shown in \autoref{fig:transporation-time}, \autoref{fig:transporation-water-one}, \autoref{fig:transporation-water-two}. There is a significant positive relationship between households possessing a private car (pcar) and households with water on the premises (watp) as shown in \autoref{fig:transporation-time}. There is also is a significant negative relationship between households possessing a private car (pcar) with households with water 30 minutes or less away round trip (tles) and households with water more than 30 minutes away round trip (tmor) with a p-value of less than 0.001. This information is essential to investigate further why this is the global trend.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:transporation-time}
\end{figure}
\autoref{fig:transporation-water-one} shows that Households possessing a motorcycle (mcyc) has a positive correlation with Households using a tube well/borehole (bore) and Households using rainwater (rain) with a p-value of less than 0.01. Similar to the previous analysis, there is a relationship between a mode of transportation to retrieve potential water sources. \autoref{fig:transporation-water-two} also shows that households possessing an animal-drawn cart (acar) have a positive and strong relationship with households using unprotected well water (uwel) with a p-value of less than 0.001. The results demonstrate that different modes of transportation factor into the accessibility of retrieving water sources on a global scale, therefore, there should be consideration of these variables to increase access to improved water sources. 
\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-water-1}
  \caption{Advanced Correlation Graph of Modes of Transportation and Water Resources}
  \label{fig:transporation-water-one}
\end{figure}

>>>>

\subsection{Model results}
First, we developed a correlation chart to quickly analyze if there is any great correlation between all the 28 numerical variables that may pertain to water accessibility. We recognized the strong and weak relationship by the size and color of the correlation plot is shown in \autoref{fig:cor-basic}, which indicates households with limited water service has the strongest and positive relationship with Households possessing a bicycle. Meanwhile, households using an improved water source has the strongest and negative relationship with households using an unimproved water source. This initial finding results indicated that the initial variables are logical and can give us insight into further understanding and the relationship between these variables.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{correlation-basic}
  \caption{Correlation Graph of Numerical Variables}
  \label{fig:cor-basic}
\end{figure}
As we continued to study further upon the correlations of the variables, we used more advanced correlation graphs to determined their p-value, and to see a relationship between different categorical variables is shown in \autoref{fig:cor-plot}, which again indicates a greater detailed comparison between the variables. Households with an improved water source on the premises have a strong relationship with households with basic water service of .84 and a p-value of less than 0.001. Also, we learned and discovered that Households using an unimproved water source have a positive relationship with Households using unprotected well water, Households using an unprotected spring, and Households using surface water with a p-value of less than 0.001 as well. These relationships justify the necessity to research further if the particular water accessibility variables can increase the accessibility of particular water sources to reach universal access to water by 2030, as proposed in the SDGs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Numerical Variables}
  \label{fig:cor-plot}
\end{figure}
Additionally, we wanted to explore if the modes of transportation variables have any relationship with potential water variables. Therefore, we investigated by developing more correlation plots relating transportation variables with water accessibility variables which are shown in \autoref{fig:transporation-time}, \autoref{fig:transporation-water-one}, \autoref{fig:transporation-water-two}. There is a significant positive relationship between households possessing a private car and households with water on the premises as shown in \autoref{fig:transporation-time}. There is also is a significant negative relationship between households possessing a private car with households with water 30 minutes or less away round trip and households with water more than 30 minutes away round trip with a p-value of less than 0.001. This information is essential to investigate further why this is the global trend.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:transporation-time}
\end{figure}
\autoref{fig:transporation-water-one} shows that Households possessing a motorcycle has a positive correlation with Households using a tube well/borehole and Households using rainwater with a p-value of less than 0.01. Similar to the previous analysis, there is a relationship between a mode of transportation to retrieve potential water sources. \autoref{fig:transporation-water-two} also shows that households possessing an animal-drawn cart have a positive and strong relationship with households using unprotected well water with a p-value of less than 0.001. The results demonstrate that different modes of transportation factor into the accessibility of retrieving water sources on a global scale, therefore, there should be consideration of these variables to increase access to improved water sources. 
\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-water-1}
  \caption{Advanced Correlation Graph of Modes of Transportation and Water Resources}
  \label{fig:transporation-water-one}
\end{figure}
